### 2013-09-18 manuscripts/reply/reply.tex
More work on reply.
Adding simulation-based exclusion assessment methods and results.

>>>>

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the methods bias towards models with smaller parameter space,
but rather allow it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa.
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret.

To better quantify the propensity of Hickerson et al.'s
\citeyear{Hickerson2013} approach to exclude the truth, we simulated
1000 pseudo-observed datasets in which the divergence times for the
22 population pairs are drawn randomly from an exponential distribution
with a mean of 0.5 ($\divt{} \sim Exp(2)$). All other parameters were
identically distributed as in the $M_1$--$M_5$ models.
We then repeated the analysis described above, using $5\e6$ prior samples from
$M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, and retaining 1,000 posterior samples
for each of the 1,000 pseudo-observed datasets.

Our results show that the model-averaging approach of \citet{Hickerson2013}
excludes the true values of parameters in 97\% of the replicates (90\% with
GLM-regression adjustment), excluding upto 21 of the 22 true divergence times
(Figure~\ref{figExclusionSimTau}.
Furthermore, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
We used a Bayes factor (comparing models that exclude the truth to those that
do not) calculated for each replicate of greater than 10 as strong support for
excluding the truth.
With that criterion, 66\% of the replicats (87\% with GLM-regression adjustment)
strongly support the exclusion of true values (Figure~\ref{figExclusionSimProb}).
